---
 #This is the basic setup of a presentation with
 #the familiar keywords from the SG style file
 documentclass: SG-ETHclass
 classoption: first, firstup, Helv, navigation
 title: Title of the talk
 author: Pavlin Mavrodiev
 date: 01.01.2014
 homepage: www.sg.ethz.ch
 institute: Chair of Systems Design
 collaborators: Vahan Nanumyan, Ingo Scholtes, Antonios Garas
 place: Zurich
 shorttitle: SG Presentation with RMarkdown 
 #specific packages needed for the presentation
 packages: pst-pdf, pst-all, amsmath, amssymb, pifont, multimedia 
 #Define the type of output -> pdf
 output: 
   beamer_presentation:    
     #include table of content
     toc: true
     fig_caption: yes
     keep_tex: yes
     pandoc_args: [
      "--template=/usr/share/texmf/tex/latex/sg-ethbeamer/SG_ETHclass.tex",
      "--filter=notefilter.py"
     ]     
 #title of the TOC slide if included. Defaults to "Contents" if not supplied
 toc_title: Agenga
 #define bibliography package, options, style and file
 natbib: yes
 #options passed to the natbib package
 natbib_options: square,numbers,sort,compress
 bibliography_style: plainnat
 bibliography_file: bibliography.bib
 biblio-title: References
 #
 setbeameroption: show notes
---

#Introduction

## R Markdown {#introduction}

- This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>. 

- You can also instert *inline* links and they look like [\color{blue} **this**](http://google.com )

- When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## More R Markdown

-- Here is a footnote[^1]. Here is a second one[^2]. Ok, and here is an inline note.^[Inline notes are easier to write, since you do not have to pick an identifier and move down to type the note.]

-- See how block quotes look like, 

> The true sign of intelligence is not knowlesge but imagination

(Albert Einshtein)

[^1]: Did you get how the footnotes work?
[^2]: Really by now you should have got it.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

# More advanced stuff

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE,fig.width=4, fig.height=4}
plot(cars)
```

## More info

1. Refer to [**this link**](<http://rmarkdown.rstudio.com/beamer_presentation_format.html>) for more information on Rmarkdown syntax in beamer presentations

2. Alternatively study the **SG_ETHclass.tex** file. It is simple enough so that you can get a pretty good idea how things work.

## Multi-column slide with notes

[begincolumns]

[column=0.5]

Some text in the first column with a code chunk
```{r}
a<-1
b<-3
a+b
```

[column=0.5]

More text in the second column

[endcolumns]

[beginnote]

1. See, we can write stuff into the notes
2. Refer to the .Rmd source file for the proper syntax
3. And we can also insert code blocks

[endnote]

----

\begin{block}{Cool block}
\begin{itemize}
\item You can input raw latex code for finer control.
\item For example, pandoc does not support markdown for the 'block' environment.
\item So you must write this in plain latex.
\end{itemize}
\end{block}

# Final words

## Citations

- If you use *biblatex* or *natbib*, pandoc will not generate a .bbl file 

- Therefore, your citations would appear as question marks

- The easisest way around is to keep the raw latex
    - use the __"keep_tex: yes"__ option
    - compile the resulting .tex file manually
    - In RStudio, this is very easy. Simply open the latex file in a separate tab and press __Compile PDF__

- Try it with this seminal publication \cite{mavrodiev2013}
